Evaluating the Performance and Energy Efficiency of the \textsc{COSMO-ART} model system

### 2014-04-25 trunk/paper_enahpc14/Sec3:Environment-setup.tex
Manuel's changes

We present here the two different  frameworks deployed on the testbed HPC systems to
measure  performance and  power  consumption of the baseline execution of COSMO-ART

@@

The \cosmoart  baseline is a  pure MPI based  Fortran~90 code
currently  running  on   distributed  multi-core  systems  only.   The
software stack on the platforms was controlled using the modules
framework which gives an easy  and flexible mechanism to access to all
of the  provided compilers, tools  and applications.  For  our initial
benchmarking,   we  opted   for   the  GNU   compiler  gcc-4.8.1   on
\monch and gcc-4.8.2 on  \pilat and \tinto) using the -O3 compiler
flag  in favor  of the  Intel compilers 14.0.1,  delivering inferior
performance.  In  addition, we installed the following implementations of MPI: MVAPICH2 1.9 on \monch and \pilat and  OpenMPI 1.6.5 on \tinto. On the other hand, we  used HDF5 1.8.12 and NetCDF  (4.3.1) libraries for  the management  of extremely  large and
complex data collections.  All computes nodes have an operating system
based on GNU/Linux featuring ``2.6.32-358.11.1.el6.x86\_64'' kernel in
\monch, ``3.0.101-0.15-default'' in \pilat and ``2.6.18-238.19.1.el5.x86\_64'' in \tinto.

>>>>

We present here the two different  frameworks deployed on the testbed HPC systems to
measure  performance and  power  consumption of the baseline execution of \cosmoart

@@

The \cosmoart  baseline is a  pure MPI based  Fortran~90 code
currently  running  on   distributed  multi-core  systems  only.   The
software stack on the platforms was controlled using the modules
framework which gives an easy  and flexible mechanism to access to all
of the  provided compilers, tools  and applications.  For  our initial
benchmarking,   we  opted   for   the  GNU   compiler  GCC 4.8.1   on
\monch and GCC 4.8.2 on  \pilat and \tinto) using the -O3 compiler
flag  in favor  of the  Intel compilers 14.0.1,  delivering inferior
performance.  In  addition, we installed the following implementations of MPI: MVAPICH2 1.9 on \monch and \pilat and  OpenMPI 1.6.5 on \tinto. On the other hand, we  used HDF5 1.8.12 and NetCDF  (4.3.1) libraries for  the management  of extremely  large and
complex data collections.  All computes nodes have an operating system
based on GNU/Linux featuring ``2.6.32-358.11.1.el6'' kernel in
\monch, ``3.0.101-0.15-default'' in \pilat and ``2.6.18-238.19.1.el5'' in \tinto.

### 2014-04-25 trunk/paper_enahpc14/Sec4:Experimental-results.tex
Manuel's changes

\begin{figure}[htbf]
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-0.eps}
  \caption{Time-to-solution and energy-to-solution comparison between
    Xeon E5 and Ivy Bridge-EP architectures}
  \label{fig:3}
\end{figure}

\begin{figure}[htbf]
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-5.eps}
  \caption{Mean time-to-solution and energy-to-solution on
    \textsc{Tintorrum} - MPI Polling and Blocking modes}
  \label{fig:4}
\end{figure}

@@

\begin{figure*}[htbf]
  \centering
  \scriptsize
  MPI polling mode\\
  \scalebox{0.5}{\input{Figs/11_12_blq0_figure.pstex_t}}\\
  MPI blocking mode\\
  \scalebox{0.5}{\input{Figs/11_12_blq1_figure.pstex_t}}
  \caption{1 hour simulation (11h-12h) trace using the MPI blocking
    mode on \textsc{Tintorrum}.}
  \label{fig:10}
\end{figure*}

\begin{figure*}[htbf]
  \centering
  \scriptsize
  MPI polling mode\\
  \scalebox{0.5}{\input{Figs/23_24_blq0_figure.pstex_t}}\\
  MPI blocking mode\\
  \scalebox{0.5}{\input{Figs/23_24_blq1_figure.pstex_t}}
  \caption{1 hour simulation (23h-24h) trace using the MPI blocking
    mode on \textsc{Tintorrum}.}
  \label{fig:11}
\end{figure*}

>>>>

\begin{figure}[htbf]
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-0.eps}
  \caption{Time-to-solution and energy-to-solution comparison between
    Xeon E5 and Ivy Bridge-EP architectures for a 24h simulation}
  \label{fig:3}
\end{figure}

\begin{figure}[htbf]
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-5.eps}
  \caption{Mean time-to-solution and energy-to-solution on
    \textsc{Tintorrum} for a 24h simulation - MPI Polling and Blocking
    modes}
  \label{fig:4}
\end{figure}

@@

\begin{figure*}[htbf]
  \centering
  \scriptsize
  MPI polling mode\\
  \scalebox{0.5}{\input{Figs/11_12_blq0_figure.pstex_t}}\\
  MPI blocking mode\\
  \scalebox{0.5}{\input{Figs/11_12_blq1_figure.pstex_t}}\\
  MPI polling mode\\
  \scalebox{0.5}{\input{Figs/23_24_blq0_figure.pstex_t}}\\
  MPI blocking mode\\
  \scalebox{0.5}{\input{Figs/23_24_blq1_figure.pstex_t}}\\
  \caption{1 hour simulation (23h-24h) trace using the MPI blocking
    mode on \textsc{Tintorrum}.}
  \label{fig:11}
\end{figure*}
